Toward dynamic models of combat or lack thereof in animal mating

### 2016-01-11 ms.tex
small changes to coeffs in the S/O DE's

Searching individuals:
\begin{equation} \label{eq:searching}
    \frac{dS}{dt} = aS -bS^2 - \frac{cS}{1+O} - eS - gO + fO
\end{equation}
Occupying individuals
\begin{equation} \label{eq:occupying}
    \frac{dO}{dt} = \frac{cS}{1+O} - eO - fO
\end{equation}

$aS - bS^2$ is individuals becoming mature.\\
$\frac{cS}{1+O}$ is searching individuals becoming occupiers through finding nests that are unoccuied.\\
$e$ is metabolic death rate\\
$f$ is the abandon rate\\
$g$ is the rate at which occupiers die in a contest\\

>>>>

Searching individuals:
\begin{equation} \label{eq:searching}
    \frac{dS}{dt} = aS - bS^2 - \frac{cS}{1+eO} - fS - hO + gO
\end{equation}
Occupying individuals:
\begin{equation} \label{eq:occupying}
    \frac{dO}{dt} = \frac{cS}{1+eO} - fO - gO
\end{equation}

$aS - bS^2$ is individuals becoming mature.\\
$\frac{cS}{1+eO}$ is searching individuals becoming occupiers through finding nests that are unoccuied.\\
$f$ is the metabolic death rate\.\
$g$ is the abandon rate.\\
$h$ is the rate at which occupiers die in a contest.\\
